\begin{minted}{protobuf}
syntax = "proto3";

package blog.api.v1;

// A service that provide blog functionalities.
service BlobService {
  option (baker.api.default_http_body_encoding) = JSON;

  // List the users in the system.
  rpc ListUsers(ListUsersRequest) returns (ListUsersResponse) {
    option (baker.api.http_path) = "/v1/users";
    option (baker.api.http_method) = GET;
  }

  // List a number of posts in the system.
  rpc ListPosts(ListPostsRequest) returns (ListPostsResponse) {
    option (baker.api.http_path) = "/v1/posts";
    option (baker.api.http_method) = GET;
  }

  // List comments of a given post.
  rpc ListPostComments(ListPostCommentsRequest) returns (ListPostCommentsResponse) {
    option (baker.api.http_path) = "/v1/posts/{post}/comments";
    option (baker.api.http_method) = GET;
  }

  // Create a post in the system.
  rpc CreatePost(CreatePostRequest) returns (Post) {
    option (baker.api.http_path) = "/v1/posts";
    option (baker.api.http_method) = POST;
  }

  // Post a comment.
  rpc PostComment(PostCommentRequest) returns (Post.Comment) {
    option (baker.api.http_path) = "/v1/posts/{comment.post_id}/comments";
    option (baker.api.http_method) = POST;
  }

  // {Dis}Like a post.
  rpc LikePost(LikePostRequest) returns (Post) {
    option (baker.api.http_path) = "/v1/posts/{post}:like";
    option (baker.api.http_method) = POST;
  }
}

// Request for `ListUsers` RPC method.
message ListUsersRequest {}

// Response for `ListUsers` RPC method.
message ListUsersResponse {
  // Users returned for the request.
  repeated User users = 1;
}

// Request for `ListPosts` RPC method.
message ListPostsRequest {
  // Return posts after a given ID.
  optional int64 after = 1;

  // Limit the number of returned posts.
  optional uint32 limit = 2;
}

// Response for `ListPosts` RPC method
message ListPostsResponse {
  // Posts returned for the request.
  repeated Post posts = 1;
}

// Request for `ListPostComments` RPC method.
message ListPostCommentsRequest {
  // ID of the post parent of the comments to return.
  int64 post = 1;

  // Returns comments after a given ID.
  optional int64 after = 2;
  // Limit the number of returned posts.
  optional uint32 limit = 2;
}

// Response for `ListPostComments` RPC method.
message ListPostCommentsResponse {
  // Comments returned for the request.
  repeated Post.Comment comments = 1;
}

// Request for `CreatePost` RPC method.
message CreatePostRequest {
  // Post to be created
  Post post = 1;
  // Author of the post
  User author = 2;
}

// Request for `PostComment` RPC method.
message PostCommentRequest {
  // Comment to be posted.
  Post.Comment comment = 1;
  // Author of the comment.
  User author = 2;
}

// Request for `LikePost` RPC method.
message LikePostRequest {
  // Post to be liked or disliked.
  int64 post = 1;
  // If set, dislike the post.
  bool dislike = 2;
}

// A user in the service.
message User {
  option (baker.orm.table_name) = "users";
  option (baker.orm.table_path) = "crate.schema.users";
  option (baker.orm.primary_key) = "user_id";

  // ID of the user.
  int64 id = 1 [
    (baker.api.field_behavior) = OUTPUT_ONLY,
    (baker.orm.column_name) = "user_id",
  ];
  // Name of the user.
  string name = 2 [ (baker.api.field_behavior) = IMMUTABLE ];

  // Idenfier of the user.
  oneof identifier {
    // The user used an email to identify himself.
    string email = 3 [ (baker.api.field_behavior) = IMMUTABLE ];
    // The user used a username to identify himself.
    string username = 4 [ (baker.api.field_behavior) = IMMUTABLE ];
  };
}

// A post in the service.
message Post {
  // A comment on a post in the service.
  message Comment {
    option (baker.orm.table_name) = "comments";
    option (baker.orm.primary_key) = "comment_id";
    option (baker.orm.table_path) = "crate.schema.comments";

    // ID of the comment.
    int64 id = 1 [
      (baker.api.field_behavior) = OUTPUT_ONLY,
      (baker.orm.column_name) = "comment_id",
    ];
    // ID of the post where this comment was posted.
    int64 post_id = 2 [
      (baker.api.field_behavior) = IMMUTABLE,
      (baker.orm.relationship) = PARENT_ID,
      (baker.orm.related_type) = "blog.api.v1.Post",
    ];
    // Author of the comment.
    int64 author_id = 3 [
      (baker.api.field_behavior) = IMMUTABLE,
      (baker.orm.relationship) = PARENT_ID,
      (baker.orm.related_type) = "blog.api.v1.User",
    ];
    // Content of the comment.
    string content = 4 [ (baker.api.field_behavior) = IMMUTABLE ];
  }

  // Possible formats of content in a Post.
  enum ContentFormat {
    option (baker.orm.database_type) = "blog.content_format";

    // Conventional default.
    UNKNOWN = 0;
    // The post was written in plain text.
    PLAIN_TEXT = 1;
    // The post was written in markdown.
    MARKDOWN = 2;
  }

  option (baker.orm.table_name) = "posts";
  option (baker.orm.primary_key) = "post_id";
  option (baker.orm.table_path) = "crate.schema.posts";

  // ID of the post.
  int64 id = 1 [
    (baker.api.field_behavior) = OUTPUT_ONLY,
    (baker.orm.column_name) = "post_id",
  ];
  // Title of the post.
  string title = 2;
  // Likes of the post.
  int32 likes = 3 [ (baker.api.field_behavior) = OUTPUT_ONLY ];
  // Dislikes of the post.
  int32 dislikes = 4 [ (baker.api.field_behavior) = OUTPUT_ONLY ];
  // Author of the post.
  int64 author_id = 5 [
    (baker.api.field_behavior) = IMMUTABLE,
    (baker.orm.relationship) = PARENT_ID,
    (baker.orm.related_type) = "blog.api.v1.User"
  ];
  // Content of the post.
  string content = 6;
  // Format used in `content`.
  ContentFormat content_format = 7;
}
\end{minted}
